Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-08-11 2_SSL_NE/article/article_supplementary.tex
added edits

Due to these limitations, any recommendations on future improvements in LED technology based on these studies are fragmented at best. Furthermore, the effect of individual innovations and technology spillovers, which has been investigated in solar PV \cite{kavlak2018evaluating}\cite{kolesnikov2020novel}\cite{nemet2019solar}, and to some extent in lithium-ion batteries \cite{Stephan_2021}, has not yet been studied in the context of lighting.

@@

Historically, the progress in LED technology has been commonly described by pointing to impressive improvements in LED device performance, more specifically device brightness, as well as electrical efficiency, and manufacturing cost reductions \cite{Taki2019}. However, metrics related to consumer experience from using white LEDs as a lighting source, such as the perceived temperature of a white light source and its ability to faithfully render colours, have also played a significant part in the market adoption of new lighting technologies \cite{Menanteau2000}\cite{Sandahl2006}\cite{CAIRD2008}\cite{murphy2012governing} and received substantial attention in LED research and development efforts \cite{azevedo2009transition,cho2017white}. Therefore, a comprehensive analysis of the evolution in white LED technology must take into consideration advances in 1) physical device performance; 2) consumer experience; and 3) LED device manufacturing costs. Next, we introduce and discuss the metrics that we use to track progress in each of these three areas.

@@

During the years following the market introduction of white LEDs, the primary metric of progress in solid-state lighting was typically luminous flux. This was because the luminous flux (total brightness) of early white LEDs was too small to allow for the economical combination of multiple LEDs into lamps for general illumination purposes. In 2000, the highest performing devices yielded around 10lm, just below the output of a candle as defined in the unit candela (1cd=12.57lm)\cite{haitz2011solid}. Progress in this metric was commonly rendered together with the associated reduction in retail prices as “Haitz’s Law”\cite{haitz1999case,haitz2011solid}. Today, however, the devices with the highest performance yield in excess of 1600lm, the equivalent of a 100W incandescent bulb \cite{cree2020bright}. LED brightness has thereby become sufficient to enable the construction of lamps from multiple LED devices, with contemporary improvements focusing instead on higher efficiency and quality of light instead of brightness. Even though a large number of scientific publications and industry periodicals continue to focus on brightness as a metric of progress in lighting, we find that, at this point in time, this metric is insufficient to capture the complexity of the multitude of efficiency improvements that have been driving overall LED efficiency \cite{weinold2021compound}. Specifically, the stagnating levels of luminous flux in the highest performing devices do not capture the outcomes of a major area of LED research, which is improving electrical efficiency at constant brightness.

@@

>>>>

Due to these limitations, any recommendations on future improvements in LED technology based on these studies are fragmented at best. Furthermore, the effect of individual innovations and technology spillovers, which has been investigated in solar PV \cite{kavlak2018evaluating,kolesnikov2020novel,nemet2019solar}, and to some extent in lithium-ion batteries \cite{Stephan_2021}, has not yet been studied in the context of lighting.

@@

Historically, the progress in LED technology has been commonly described by pointing to impressive improvements in LED device performance, more specifically device brightness, as well as electrical efficiency, and manufacturing cost reductions \cite{Taki2019}. However, metrics related to consumer experience from using white LEDs as a lighting source, such as the perceived temperature of a white light source and its ability to faithfully render colours, have also played a significant part in the market adoption of new lighting technologies \cite{Menanteau2000,Sandahl2006,CAIRD2008,murphy2012governing} and received substantial attention in LED research and development efforts \cite{azevedo2009transition,cho2017white}. Therefore, a comprehensive analysis of the evolution in white LED technology must take into consideration advances in 1) physical device performance; 2) consumer experience; and 3) LED device manufacturing costs. Next, we introduce and discuss the metrics that we use to track progress in each of these three areas.

@@

During the years following the market introduction of white LEDs, the primary metric of progress in solid-state lighting was typically luminous flux. This was because the luminous flux (total brightness) of early white LEDs was too small to allow for the economical combination of multiple LEDs into lamps for general illumination purposes. In 2000, the highest performing devices yielded around 10lm, just below the output of a candle as defined in the unit candela (1cd=12.57lm)\cite{haitz2011solid}. Progress in this metric was commonly rendered together with the associated reduction in retail prices as “Haitz’s Law” \cite{haitz1999case,haitz2011solid}. Today, however, the devices with the highest performance yield in excess of 1600 lm, the equivalent of a 100 W incandescent bulb \cite{cree2020bright}. LED brightness has thereby become sufficient to enable the construction of lamps from multiple LED devices, with contemporary improvements focusing instead on higher efficiency and quality of light instead of brightness. Even though a large number of scientific publications and industry periodicals continue to focus on brightness as a metric of progress in lighting, we find that, at this point in time, this metric is insufficient to capture the complexity of the multitude of efficiency improvements that have been driving the overall LED efficiency \cite{weinold2021compound}. Specifically, the stagnating levels of luminous flux in the highest performing devices do not capture the outcomes of a major area of LED research, which is improving electrical efficiency at constant brightness.

@@

\section{Methodological Details}

This Supplementary Note provides additional details for the main methods and data sources used in our mixed-methods research approach described in the Methods section in the main text.

\subsection{Background of Interviewed Experts}

\begin{table}[H]
\small
    \centering
    \caption{Anonymized list of interviewed LED experts.}
    \vspace{5mm}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
        \textit{\#} & \textit{Sector} & \textit{Role} & \textit{Country} & \textit{Expertise} \\ \hline
        1 & Academia & Senior researcher & UK & Epitaxy \\ \hline
        2 & Industry & Consultant, former senior researcher & USA & Device architecture \\ \hline
        3 & Industry & Consultant, former head of R\&D & Germany & Epitaxy \\ \hline
        4 & Academia & Professor & Austria & Phosphors \\ \hline
        5 & Industry & Consultant, former head of R\&D & USA & Device architecture \\ \hline
        6 & Consulting & Consultant, former senior technical advisor & USA & Device architecture \\ \hline
        7 & Academia & Professor & Germany & Phosphors \\ \hline
        8 & Government & R\&D manager & USA & Device architecture \\ \hline
        9 & Consulting & Consultant & USA & Device applications \\ \hline
        10 & Academia & Professor & France & Device physics \\ \hline
        11 & Industry & Senior scientist, former head of R\&D & USA & Device architecture \\ \hline
        12 & Industry & Principal scientist & Germany & Phosphors \\ \hline
        13 & Industry & Former head of R\&D & USA & Phosphors \\ \hline
    \end{tabular}
    \label{tab:interviews}
\end{table}
